---
title: "final"
author: "Jiawei Zhang"
date: "4/21/2019"
output: html_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4,fig.align = 'center', warning=FALSE, message=FALSE,echo=FALSE,results='hold')
```

```{r}
library(dplyr)
library(psych)
library(car)
library(caret)
library(corrplot)
library(ggplot2)
library(pROC)
library(plotROC)
library(rpart.plot)
library(knitr)
library(gbm)
library(rpart) # tree based model 
library(MASS)
library(caTools)
```

#####1. Data Manipulation
```{r}
options(scipen = 6)
rawdata<-read.csv('/Users/jiawei/Desktop/second\ sem/big\ data2/final/WA_Fn-UseC_-Telco-Customer-Churn.csv')
#fill NA with decision tree model
fitrpart <- rpart(TotalCharges ~ .,data=rawdata[!is.na(rawdata$TotalCharges),c(-1,-21)], method="anova")
data<-rawdata
data[is.na(data$TotalCharges),]$TotalCharges<-predict(fitrpart,data[is.na(data$TotalCharges),c(-1,-21)])
#factor seniorsitizen for it's int
data$SeniorCitizen<-as.factor(data$SeniorCitizen)
#delete customer id
data<-data[,-1]
#combine 'no xx service' into 'no' category
data[,7]<- as.factor(gsub("No phone service", "No", data[,7]))
data[,c(9:14)] <- data.frame(lapply(data[,c(9:14)], function(x) {gsub("No internet service", "No", x)}))

#add tenure_year: combine customer into group(by tenure year) for visulization, not used in model
data<- mutate(data, tenure_year = tenure)
data$tenure_year[data$tenure_year >=0 & data$tenure_year <= 12] <- '0-1 year'
data$tenure_year[data$tenure_year > 12 & data$tenure_year <= 24] <- '1-2 years'
data$tenure_year[data$tenure_year > 24 & data$tenure_year <= 36] <- '2-3 years'
data$tenure_year[data$tenure_year > 36 & data$tenure_year <= 48] <- '3-4 years'
data$tenure_year[data$tenure_year > 48 & data$tenure_year <= 60] <- '4-5 years'
data$tenure_year[data$tenure_year > 60 & data$tenure_year <= 72] <- '5-6 years'
data$tenure_year<-as.factor(data$tenure_year)
#scale 3 numerical vats
datap<-data
for(i in c(5,18,19)){data[,i]=scale(data[,i])}
```
only total charges has missing values (0.15%), use rpart algo to fill the NA (assume they miss at random)
'no internet serveice' in variable 'OnlineSecurity', 'OnlineBackup', 'DeviceProtection','TechSupport','StreamingTV', 'StreamingMovies. combine 'no internet service' with 'no' catgory


#####3. Data preprocessin
```{r}
#turn categorical var into dummys
data_final1<-data %>% mutate(
  InternetService_fiber_optic=ifelse(data$InternetService=='Fiber optic','yes','no'),
  InternetService_no=ifelse(data$InternetService=='No','yes','no'),
  contract_1year=ifelse(data$Contract=='One year','yes','no'),
  contract_2year=ifelse(data$Contract=='Two year','yes','no'),
   PaymentMethod_creditcard=ifelse(data$PaymentMethod=='Credit card (automatic)','yes','no'),
   PaymentMethod_Ele_check=ifelse(data$PaymentMethod=='Electronic check','yes','no'),
  PaymentMethod_mailed_check=ifelse(data$PaymentMethod=='Mailed check','yes','no'),
  tenure12yr=ifelse(data$tenure_year=='1-2 years','yes','no'),
  tenure23yr=ifelse(data$tenure_year=='2-3 years','yes','no'),
  tenure34yr=ifelse(data$tenure_year=='3-4 years','yes','no'),
  tenure45yr=ifelse(data$tenure_year=='4-5 years','yes','no'),
    tenure56yr=ifelse(data$tenure_year=='5-6 years','yes','no')
  
)
data_final<-data_final1[,-c(8,15,17,21,29:33)]
for(i in 18:24){
data_final[,i]<-as.factor(data_final[,i])}
write.csv(data_final,'data_final.csv')
```


#####4. Model
#####4.1 logistic
```{r}
set.seed(12)
trainindex<-sample(1:nrow(data_final),round(0.8*nrow(data_final)))
train<-data_final[trainindex,]
test<-data_final[-trainindex,]

model1 <- glm(Churn ~ ., data =train, family = "binomial")
summary(model1)
#find the best model with lowest AIC
model2<-stepAIC(model1,direction = "both")
summary(model2)
#delete var not in best model
train_logit<-train[,-c(1,3,6,9,10,22,24)]
data_logit<-data_final[,-c(1,3,6,9,10,22,24)]

#actually model3=model2
model3 <- glm(Churn ~ ., data = train_logit, family = "binomial")
summary(model3)

#use cv to test model using train data
control <- trainControl(method="cv",number=5,savePredictions = T, summaryFunction = twoClassSummary,classProbs = T) 
set.seed(11)
logit <- train(Churn~., data=train_logit, method="glm", trControl=control)
summary(logit)

#use test data
pred <- predict(logit, type = "prob", newdata = test[,-17])
actual_churn<-test[,17]

#draw cutoff-sen,spe,accuracy plot
#function of calculate sen,spe,acc at different cutoff
perform_fn <- function(pred,actual) 
{
  cutoff<- seq(0.01,1.00,length=100)
  OUT = data.frame(0,100,4)
  for(i in cutoff)
  {
  predicted_churn <- factor(ifelse(pred$Yes >= i, "Yes", "No"))
  conf <- confusionMatrix(predicted_churn, actual, positive = "Yes")
  OUT[i*100,3] <- conf$overall[1]
  OUT[i*100,1]  <- conf$byClass[1]
  OUT[i*100,2]  <- conf$byClass[2]
  OUT[i*100,4]  <-i
  }
  colnames(OUT)<- c( "accuracy","sensitivity", "specificity",'cutoff')
  return(OUT)
}


OUT<-perform_fn(pred,actual_churn)

cutoffplot<-function(OUT,cutoff=1)
{
p<-ggplot(data=OUT,aes(x=OUT[,4]))+
  geom_line(aes(y=OUT[,1],colour='Sensitivity'),lwd=.7)+
  geom_line(aes(y=OUT[,2],color="Specificity"),lwd=.7)+
   geom_line(aes(y=OUT[,3],color='Accuracy'),lwd=.7)+
  geom_vline(xintercept=cutoff, linetype="dashed")+
  scale_colour_manual(breaks = c('Sensitivity', "Specificity", "Accuracy"),
                      values = c("black", '#CD040B', "blue")) +
  labs(title='',x='Cutoff',y='Value')
 return(p)
}
cutoffplot(OUT,0.25)

```
logistic regression
use Stepaic to find the model with lowest AIC.

True positive vs Ture negative, which is more important?
TP high, TN low: high cost(because of promotion, activities to retain churn customer, etc)
TP low, TN high:  low revenue(people leave)


#####4.2 knn
```{r}
train<-data[trainindex,]
test<-data[-trainindex,]
set.seed(11)
knn<-train(Churn~., data=train, method="knn",preProcess=c('center',"scale"), trControl=control,tuneLength = 50)
pred <- predict(knn, type = "prob", newdata = test[,-20])
actual_churn<-test[,20]
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT,0.25)


```
best k=75
accuracy=0.8362105


#####4.3 decision tree
```{r}
set.seed(11)
dt <- train(Churn~., data=train, method="rpart", preProcess=c('center',"scale"), trControl=control)
#model5
#summary(model5)

pred <- predict(dt, type = "prob", newdata = test[,-20])
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT)


selectedIndices <- dt$pred$cp ==dt$bestTune
p1<-ggplot(dt$pred[selectedIndices,], aes(m=Yes, d=factor(obs, levels = c('Yes', "No")))) + 
  geom_roc(n.cuts=0) + 
  coord_equal() +
  style_roc()

rpart.plot(dt$finalModel)
```



#####4.3 ramdom forest
```{r}
set.seed(11)
rf<-train(Churn~., data=train, method="rf",preProcess=c('center',"scale"), trControl=control)
pred <- predict(rf, type = "prob", newdata = test[,-20])
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT)

```

#####4.4 naive bayes
```{r}
set.seed(11)
nb<-train(Churn~., data=train, method="nb",preProcess=c('center',"scale"), trControl=control)
pred <- predict(nb, type = "prob", newdata = test[,-20])
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT)


qda<-train(Churn~., data=train, method="qda",preProcess=c('center',"scale"), trControl=control)
pred <- predict(qda, type = "prob", newdata = test[,-20])
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT)


```

#####4.5 xgb
```{r}
set.seed(11)
xgbtree<-train(Churn~., data=train, method="xgbTree",preProcess=c('center',"scale"), trControl=control)
pred <- predict(xgbtree, type = "prob", newdata = test[,-20])
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT)

```

#####4.5 svm
```{r}
set.seed(11)
svm<-train(Churn~., data=data, method="svmRadial",preProcess=c('center',"scale"), trControl=control)
pred <- predict(svm, type = "prob", newdata = test[,-20])
OUT<-perform_fn(pred,actual_churn)
cutoffplot(OUT,0.15)
#colAUC(pred,test[,-20]$Churn,plotROC = TRUE)
```

#####5. Visulization

```{r eval=FALSE, include=FALSE}
ggplot(data,aes(x=SeniorCitizen,y=MonthlyCharges))+geom_boxplot()+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x=SeniorCitizen,fill=InternetService))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700','black'))


ggplot(data,aes(x=gender,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= SeniorCitizen ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x=  Partner  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(data,aes(x= Dependents ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(data,aes(x= PhoneService  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= MultipleLines ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(data,aes(x= InternetService ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= OnlineSecurity  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= OnlineBackup  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= DeviceProtection ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= TechSupport  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x=StreamingTV  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= StreamingMovies ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x=  Contract  ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= PaperlessBilling ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= PaymentMethod ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(data,aes(x= tenure_year ,fill=Churn))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(datap,aes(x= tenure ,fill=Churn))+geom_density(alpha=0.6)+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(datap,aes(x= MonthlyCharges ,fill=Churn))+geom_density(alpha=0.6)+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(datap,aes(x= TotalCharges ,fill=Churn))+geom_density(alpha=0.6)+
  scale_fill_manual(values=c('#CD040B','#FFD700'))
ggplot(datap,aes(y= MonthlyCharges ,fill=Churn))+geom_boxplot()+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(datap,aes(y= TotalCharges ,fill=Churn))+geom_boxplot()+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(datap,aes(x=MonthlyCharges,y=TotalCharges,col=tenure_year))+
  geom_point(size=.5)
ggplot(datap,aes(x=MonthlyCharges,y=TotalCharges,col=Churn))+
  geom_point(size=.5)+
  scale_color_manual(values=c('#CD040B','#FFD700'))

data1<-datap
data1[data1$tenure==0,]$tenure=1
data1<-datap %>% group_by(Churn,tenure_year) %>% 
  summarize(Month_avg_charge=mean(TotalCharges/tenure))
ggplot(data1,aes(x=tenure_year,y=Month_avg_charge,fill=Churn))+
  geom_bar(stat= "identity",position = 'fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700'))

ggplot(data,aes(x=SeniorCitizen,fill= StreamingMovies ))+geom_bar(position='fill')+
  scale_fill_manual(values=c('#CD040B','#FFD700','black'))

```

